Data- and Systems Paper: Identifying Handicap Parking Spots for Event's Venues

### 2016-04-09 milestone1/paper/paper.tex
added web app discussion [mls1]

The web application may be improved by provided extended support. New queries may be added. %TODO finish this

>>>>

The Web application may be improved by provided extended support. Screenshots of
the application are shown in Figure \ref{fig:app}. First the user is presented with
the list of venues (Figure \ref{fig:app-venues}). By clicking on a row of the table
the user is presented with the contents of Figure \ref{fig:app-slots}. This page
shows a list of 20 parking slots sorted by distance from the queried venue.

We developed the queries based on geographical distance (using decimal latitude
and longitude) using a mathematical formula. This may result in numerical errors
and therefore wrong results. An immediate improvement of the system would be to
use Stardog's support for geospatial queries. Then querying for geospatial
relations like \texttt{geof:relate}, \texttt{geof:distance},
\texttt{geof:within}, \texttt{geof:nearby} and
\texttt{geof:area}\footnote{The \texttt{geof} namespace defines geospatial
functions at the URL \url{http://www.opengis.net/def/function/geosparql/}}.
